Physical Characteristics Required of a Millisecond Pulsar Population to Reproduce the Galactic Center Excess

### 2021-07-07 paper/draft.tex
Answering questions

\section{Methods \& Datasets}
\subsection{GCE Spacial distribution}
We model the spacial distribution of MSPs in the GC with an NFW squared profile, to match with empirical data. The number density of an NFW profile is spherically symmetric, with radial density profile
\label{sec:spacial-distro}
\begin{equation}
    \rho_\text{NFW}(r) \propto \parens{\frac{r}{r_s}}^{-\gamma}\parens{1 + \frac{r}{r_s}}^{-3+\gamma}
    \label{eqn:nfw}
\end{equation}
where $\gamma = 1.2$ and $r_s = \SI{20}{\kilo\parsec}$ for this work. Other sources occasionally use $\gamma = 1$.
\comment{The flux that comes from this NFW profile is unnormalizable. For most of the project, that doesn't matter because (l, b) = 0 is cut out. But for converting between ROIs, it means my former method was invalid.}

@@

$N_\text{r}$ and $R_\text{r}$ have been studied by \comment{Some technical name for the Fermilab team.} \cite{Zhong:2019ycb}. The authors performed a template fit to data from Fermi-LAT to isolate spacial peaks in flux, finding 110 \comment{(I got 110; their paper says 107)} peaks within 0.3$^\circ$ of a source in the 4FGL catalog within the region of interest \cite{Abdollahi_2020}. Of these 110 sources, they exclude all that are listed in the 4FGL catalog as not associated with pulsars. Of those that are known to be pulsars, they exclude all whose positions are known not to be within $\SI{2}{\kilo\parsec}$ of the GC via the ATNF Pulsar Catalog \cite{Hobbs04}. This leaves 47 point sources in the 4FGL catalog whose origins are either known to be pulsars in the GC or are unknown. We will therefore set $N_\text{r} = 47$ for this paper. If the allowed distance between a flux peak and a 4FGL source is extended from 0.3$^\circ$ to $0.55^\circ$, five more sources are added. Together, the 47 sources are responsible for $R_\text{r}=0.2$ of the total GCE flux. \comment{Shouldn't I actually redo this addition given the fact that I'm now not using the same GCE flux as Fermilab?} These 47+5 sources used here are displayed in figure \ref{fig:47-sources}.

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figs/point-source-positions.pdf}
    \caption{The 47 point sources within $0.3^\circ$ of a 4FGL source. Also shown are the 5 sourecs added by extending to $0.55^\circ$ separation. The sources are scaled by luminosity in radius. The gray band represents the $|b| \leq 2^\circ$ cut made around the galactic disk.}
    \label{fig:47-sources}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{figs/total-flux-bars.pdf}
    \caption{Total flux of the GCE as determined by the three integration methods discussed. \comment{Here I would discuss why Ajello doesn't have a value for the power law case if this is still true once I have the original source}.}
    \label{fig:total-flux-bars}
\end{figure}

@@

Ref. \cite{Ploeg:2020jeh} proposes a more intricate luminosity function, derived from a model of the pulsars themselves. They find that differences in spectrum between resolved, globular cluster MSPs in the Galactic disk and unresolved MSPs at the Galactic center are not significant. Their luminosity function generated for the galactic disk closely resembles a log normal luminosity function as in equation, where $L_0 = \SI{1.61e+32}{\erg\per\second}$ and $\sigma=0.700$ were obtained from a least-squares fit with $p$-value very close to 1\comment{Is there something wrong with the error bars here?}.

@@

Finally, ref. \cite{Lee:2015fea} proposes a broken-power law luminosity function of
\begin{equation}
    P_\text{NPTF}(L) = \parens{\frac{\parens{1-n_1}\parens{1-n_2}}{L_b \parens{n_1 - n_2}}}\begin{cases}
        \parens{\fraci{L}{L_\text{b}}}^{-n_{1}} & L < L_{b} \\
        \parens{\fraci{L}{L_\text{b}}}^{-n_{2}} & L > L_b
    \end{cases}
    \label{eqn:nptf}
\end{equation}
where the free parameters  $n_1$, $n_2$, and $L_b$ were found via a Non-Poissonian Template Fitting model (NPTF) to be $(18.2, -0.66, \SI{8.66e+33}{\erg\per\second})$ for an NFW-squared-distributed population of MSPs named NFW PS. The paper proposes a second luminosity function named Disk PS with parameters $(17.5, 1.4, \SI{3.34e+35}{\erg\per\second})$, which is unnormalizable except when a minimum luminosity of pulsars $L_\text{min}$ is introduced. \comment{I will want to remove the unnormalizable one. When should I do it?} The luminosity-valued parameters were originally given as fluxes in $\SI{}{\photon \per \centi\meter\squared \per \second}$. The photon energy was calculated via appendix \ref{app:photon-energy} and the flux converted to luminosity via appendix \ref{app:lum-to-flux}.

@@

\subsection{Sensitivity Models}
\label{sec:sensitivity}
\comment{Should I name these Model A, Model B, Model C, or keep the descriptive but vague names? Which is easier to follow?} The \textit{Fermi} telescope does not detect every pulsar in the GC; background emission obscures dimmer pulsars, and statistical effects cause some brighter sources to be unresolved. We make use of three sensitivity models to account for these factors.

@@

\section{Results}
\subsection{$N_\text{r}$, $R_\text{r}$, and $N_\text{GCE}$ for different luminosity functions}
Using each of the luminosity functions outlined in section \ref{sec:sensitivity}, we extract the total number of resolvable MSPs $N_\text{r}$, the ratio of the flux received from those resolved MSPs to the total flux of the GCE $R_\text{r}$, and the total number of MSPs $N_\text{GCE}$ by forcing each function to reproduce the observed flux of the GCE. This is done for many parameterizations of the power law and log normal luminosity functions (eqs. \ref{eqn:power-law} and \ref{eqn:log-normal}), with $N_\text{GCE}$ displayed as a contour map in figures \ref{fig:step-function} and \ref{fig:position-dependent}, using the step function and the position-dependent sensitivity models respectively. The observations $N_\text{r}=47$ and $R_\text{r}=0.2$ trace out a one-parameter family of luminosity functions that is also displayed. Since some resolved sources may not in fact be part of the GC, the regions with $N_\text{r} < 47$ and $R_\text{r} < 0.2$ also satisfy observational constraints and are marked.

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{figs/power-law-step.pdf}
        \includegraphics[width=\textwidth]{figs/power-law-alpha-step.pdf}
        \includegraphics[width=\textwidth]{figs/log-normal-step.pdf}
        \caption{Step function sensitivity model}
        \label{fig:step-function}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{figs/power-law-pos-1x.pdf}
        \includegraphics[width=\textwidth]{figs/power-law-alpha-pos-1x.pdf}
        \includegraphics[width=\textwidth]{figs/log-normal-pos-1x.pdf}
        \caption{Position dependent sensitivity model}
        \label{fig:position-dependent}
    \end{subfigure}
    \caption{$N_\text{r}$, $R_\text{r}$, and $N_\text{GCE}$ calculations generated for parameterizations of a power law luminosity function (top two plots) and log normal (bottom plots). The parameterizations used in other analyses are marked. Regions allowed by the $N_\text{r} \leq 47$ and $R_\text{r} \leq 0.2$ are marked with \texttt{|} and \texttt{-} respectively, while regions allowed by both constraints are marked with \texttt{+}. The top power law plot (blue) fixes $\alpha=1.94$ while the lower (green) fixes $L_\text{min}=\SI{1e29}{erg\per\second}$}
    \label{fig:step-and-pos}
\end{figure}

@@

    \begin{subtable}[h]{\textwidth}
        \centering
        \begin{tabular}{|p{4cm} >{\centering\arraybackslash}p{2cm} >{\centering\arraybackslash}p{2cm} >{\centering\arraybackslash}p{2cm}|}
            Power law & 5.38 & 0.0449 & $\num{5.91e6}$ \\
            Log normal, GCL & 79.9 & 0.683 & 473 \\
            Log normal, GCE & 13.5 & 0.0649 & $\num{1.90e4}$ \\
            Log normal, AIC & 59.4 & 0.518 & $\num{2.99e3}$ \\
            NFW NPTF & 0 & 0 & $\num{0}$ \\
            DISK NPTF & 0 & 0 & $\num{0}$ \\
            \hline
        \end{tabular}
        \caption{Smoothed sensitivity model}
        \label{tab:smoothed-results}
    \end{subtable}
    \caption{Number of resolved point sources, ratio of resolved flux to total flux, and total number of point sources predicted to make up the GCE based on six luminosity function parameterizations and the requirement that the point sources reproduce the entire flux of the GCE. For definitions of the parameterizations, see section \ref{sec:lum-funcs}.}
    \label{tab:specific-results}
\end{table}

@@

\subsection{Sensitivity models}
Figure \ref{fig:step-and-pos} and table \ref{tab:specific-results} both demonstrate that the step function and position-dependent sensitivity models yield starkly different observables. The regions of allowed parameterization differ greatly, especially in the power law case, between the two models, and predictions for $N_\text{r}$ can differ by as much as a factor of ten for specific parameterizations. Predictions by $R_\text{r}$ differ by as much as a factor of three. This is in part because bright pulsars distant from Earth have lower flux, and therefore can appear unresolved in the position-dependent sensitivity model, but the step function sensitivity model always marks these pulsars as unresolved. The difference is also caused by the fact that lower sensitivity is correlated with MSP population density, a fact not appreciated by the step function model. The GCE log normal luminosity function differs most between sensitivity models, most likely due to \comment{it's thinness and low mean, but I need to think more about exactly why this is.}

@@

In contrast, the smoothed sensitivity model does not appear to differ from the position-dependent sensitivity model by nearly as much. \comment{Except the power law, which may be a bug?} This is likely because the smoothed sensitivity model differs from the position dependent model only for MSPs near $F_\text{th}(\ell, b)$, which is a relatively small number of MSPs for most luminosity functions. Motivated by this similarity and the greater computational complexity of the smoothed sensitivity model, we will mostly use the position-dependent sensitivity model throughout the rest of this study.

@@

Plots of $N_\text{r}$, $R_\text{r}$, and $N_\text{GCE}$ for different parameterizations of the power law and log normal luminosity functions are shown in figure \ref{fig:sensitivity-results}, and values for $N_\text{r}$ and $R_\text{r}$ for specific parameterizations are given in table \ref{tab:sensitivity-values}. The number of sources in the GCE does not depend on the telescope's sensitivity, so $N_\text{GCE}$ is not included in table \ref{tab:sensitivity-values} and is only included in fig. \ref{fig:sensitivity-results} for reference. \comment{That means that the backgrounds of the column plots do not change from plot to plot. I could put them all on the same thing.}

@@

The flux ratio as computed by equation \ref{eqn:roi-conversion} between our region and the same $40^\circ \times 40^\circ$ without the Galactic disk cutout is 2.10. Similarly, the ratio is 1.64, 1.27, 0.915, and 1.013 \comment{Wrong!} for a $30^\circ \times 30^\circ $, $20^\circ \times 20^\circ$, $10^\circ \times 10^\circ$, and $7^\circ \times 7^\circ$ respectively.

@@

\section{Calculation of photon energy}
\label{app:photon-energy}
The parameterization of the NPTF luminosity function of ref. \cite{Lee:2015fea} is given with flux units of photons per second. To convert this to luminosity via appendix \ref{app:lum-to-flux}, we need to find the energy of a single GCE photon. To do this, we fit a broken power law to the GCE spectrum found by di Mauro and described in section \ref{sec:total-lum}, defining the flux observed from photons in an energy bin of energy $E_\gamma$ and width $dE_\gamma$ as $dF = E_\gamma N(E_\gamma)dE_\gamma$. The function $E_\gamma N(E_\gamma)$ is plotted in figure \ref{fig:di-mauro-example}. The average photon energy is then calculated by
\begin{equation}
    \langle E_\gamma \rangle =  \brackets{\int_{\SI{0.1}{\giga\electronvolt}}^{\SI{100}{\giga\electronvolt}} E_\gamma N(E_\gamma) dE_\gamma} \brackets{\int_{\SI{0.1}{\giga\electronvolt}}^{\SI{100}{\giga\electronvolt}} N(E_\gamma) dE_\gamma}^{-1} = \SI{0}{\giga\electronvolt}.
    \label{eqn:photon-energy}
\end{equation}
\comment{I'd like to finish this. Give examples of photon energy.}

@@

\bibliographystyle{plain}
\bibliography{gce.bib}

>>>>

\section{Methods \& Datasets}
\subsection{GCE Spacial distribution}
We model the spacial distribution of MSPs in the GC with an NFW squared profile, to match with empirical data. The number density of an NFW profile is spherically symmetric, with radial density profile
\label{sec:spacial-distro}
\begin{equation}
    \rho_\text{NFW}(r) \propto \parens{\frac{r}{r_s}}^{-\gamma}\parens{1 + \frac{r}{r_s}}^{-3+\gamma}
    \label{eqn:nfw}
\end{equation}
where $\gamma = 1.2$ and $r_s = \SI{20}{\kilo\parsec}$ for this work. Other sources occasionally use $\gamma = 1$.

@@

$N_\text{r}$ and $R_\text{r}$ have been studied by \comment{Some technical name for the Fermilab team.} \cite{Zhong:2019ycb}. The authors performed a template fit to data from Fermi-LAT to isolate spacial peaks in flux, finding 107 unique peaks within 0.3$^\circ$ of a source in the 4FGL catalog within the region of interest \cite{Abdollahi_2020}. Of these sources, they exclude all that are listed in the 4FGL catalog as not associated with pulsars. Of those that are known to be pulsars, they exclude all whose positions are known not to be within $\SI{2}{\kilo\parsec}$ of the GC via the ATNF Pulsar Catalog \cite{Hobbs04}. This leaves 47 point sources in the 4FGL catalog whose origins are either known to be pulsars in the GC or are unknown. We will therefore set $N_\text{r} = 47$ for this paper. If the allowed distance between a flux peak and a 4FGL source is extended from 0.3$^\circ$ to $0.55^\circ$, five more sources are added. Together, the 47 sources are responsible for $R_\text{r}=0.2$ of the total GCE flux. \comment{Shouldn't I actually redo this addition given the fact that I'm now not using the same GCE flux as Fermilab?} These 47+5 sources used here are displayed in figure \ref{fig:47-sources}.

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figs/point-source-positions.pdf}
    \caption{The 47 point sources within $0.3^\circ$ of a 4FGL source. Also shown are the 5 sourecs added by extending to $0.55^\circ$ separation. The sources are scaled by luminosity in radius. The gray band represents the $|b| \leq 2^\circ$ cut made around the galactic disk. \comment{I think this disagrees with the Fermilab paper}}
    \label{fig:47-sources}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{figs/total-flux-bars.pdf}
    \caption{Total flux of the GCE as determined by the three integration methods discussed.}
    \label{fig:total-flux-bars}
\end{figure}

@@

Ref. \cite{Ploeg:2020jeh} proposes a more intricate luminosity function, derived from a model of the pulsars themselves. They find that differences in spectrum between resolved, globular cluster MSPs in the Galactic disk and unresolved MSPs at the Galactic center are not significant. Their luminosity function generated for the galactic disk closely resembles a log normal luminosity function as in equation, where $L_0 = \SI{1.61e+32}{\erg\per\second}$ and $\sigma=0.700$ were obtained from a least-squares fit with $p$-value very close to 1.

@@

Finally, ref. \cite{Lee:2015fea} proposes a broken-power law luminosity function of
\begin{equation}
    P_\text{NPTF}(L) = \parens{\frac{\parens{1-n_1}\parens{1-n_2}}{L_b \parens{n_1 - n_2}}}\begin{cases}
        \parens{\fraci{L}{L_\text{b}}}^{-n_{1}} & L < L_{b} \\
        \parens{\fraci{L}{L_\text{b}}}^{-n_{2}} & L > L_b
    \end{cases}
    \label{eqn:nptf}
\end{equation},
where the free parameters  $n_1$, $n_2$, and $L_b$ were found via a Non-Poissonian Template Fitting model (NPTF) to be $(18.2, -0.66, \SI{9.13e+33}{\erg\per\second})$ for an NFW-squared-distributed population of MSPs named NFW PS. The paper proposes a second luminosity function named Disk PS with parameters $(17.5, 1.4, \SI{3.53e+35}{\erg\per\second})$, which is unnormalizable except when a minimum luminosity of pulsars $L_\text{min}$ is introduced. The luminosity-valued parameters were originally given as fluxes in $\SI{}{\photon \per \centi\meter\squared \per \second}$. The photon energy was calculated via appendix \ref{app:photon-energy} and the flux converted to luminosity via appendix \ref{app:lum-to-flux}.

@@

\subsection{Sensitivity Models}
\label{sec:sensitivity}
The \textit{Fermi} telescope does not detect every pulsar in the GC; background emission obscures dimmer pulsars, and statistical effects cause some brighter sources to be unresolved. We make use of three sensitivity models to account for these factors.

@@

\section{Results}
\subsection{$N_\text{r}$, $R_\text{r}$, and $N_\text{GCE}$ for different luminosity functions}
Using each of the luminosity functions outlined in section \ref{sec:sensitivity}, we extract the total number of resolvable MSPs $N_\text{r}$, the ratio of the flux received from those resolved MSPs to the total flux of the GCE $R_\text{r}$, and the total number of MSPs $N_\text{GCE}$ by forcing each function to reproduce the observed flux of the GCE. This is done for many parameterizations of the power law and log normal luminosity functions (eqs. \ref{eqn:power-law} and \ref{eqn:log-normal}), with $N_\text{GCE}$ displayed as a contour map in figures \ref{fig:step-function} and \ref{fig:position-dependent}, using the step function and the position-dependent sensitivity models respectively. The first row of these figures varies $L_\text{min}$ and $L_\text{max}$, with $\alpha=1.94$, which is the value computed by ref. \cite{Zhong:2019ycb}; the second row varies $L_\text{max}$ and $\alpha$, with $L_\text{min}=\SI{1e29}{\erg\per\second}$. The observations $N_\text{r}=47$ and $R_\text{r}=0.2$ trace out a one-parameter family of luminosity functions that is also displayed. Since some resolved sources may not in fact be part of the GC, the regions with $N_\text{r} < 47$ and $R_\text{r} < 0.2$ also satisfy observational constraints and are marked.

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{figs/power-law-step.pdf}
        \includegraphics[width=\textwidth]{figs/power-law-alpha-step.pdf}
        \includegraphics[width=\textwidth]{figs/log-normal-step.pdf}
        \caption{Step function sensitivity model}
        \label{fig:step-function}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{figs/power-law-pos-1x.pdf}
        \includegraphics[width=\textwidth]{figs/power-law-alpha-pos-1x.pdf}
        \includegraphics[width=\textwidth]{figs/log-normal-pos-1x.pdf}
        \caption{Position dependent sensitivity model}
        \label{fig:position-dependent}
    \end{subfigure}
    \caption{$N_\text{r}$, $R_\text{r}$, and $N_\text{GCE}$ calculations generated for parameterizations of a power law luminosity function (top two plots) and log normal (bottom plots). The parameterizations used in other analyses are marked. Regions allowed by the $N_\text{r} \leq 47$ and $R_\text{r} \leq 0.2$ are marked with \texttt{|} and \texttt{-} respectively, while regions allowed by both constraints are marked with \texttt{+}. The top power law plot (blue) fixes $\alpha=1.94$ while the lower (green) fixes $L_\text{min}=\SI{1e29}{erg\per\second}$.}
    \label{fig:step-and-pos}
\end{figure}

@@

    \begin{subtable}[h]{\textwidth}
        \centering
        \begin{tabular}{|p{4cm} >{\centering\arraybackslash}p{2cm} >{\centering\arraybackslash}p{2cm} >{\centering\arraybackslash}p{2cm}|}
            Power law & 5.35 & 0.0448 & $\num{5.91e6}$ \\
            Log normal, GCL & 79.9 & 0.683 & 473 \\
            Log normal, GCE & 13.5 & 0.0649 & $\num{1.90e4}$ \\
            Log normal, AIC & 59.4 & 0.518 & $\num{2.99e3}$ \\
            NFW NPTF & 0 & 0 & $\num{0}$ \\
            DISK NPTF & 0 & 0 & $\num{0}$ \\
            \hline
        \end{tabular}
        \caption{Smoothed sensitivity model}
        \label{tab:smoothed-results}
    \end{subtable}
    \caption{Number of resolved point sources, ratio of resolved flux to total flux, and total number of point sources predicted to make up the GCE based on six luminosity function parameterizations and the requirement that the point sources reproduce the entire flux of the GCE. For definitions of the parameterizations, see section \ref{sec:lum-funcs}.}
    \label{tab:specific-results}
\end{table}

@@

\subsection{Sensitivity models}
Figure \ref{fig:step-and-pos} and table \ref{tab:specific-results} both demonstrate that the step function and position-dependent sensitivity models yield starkly different observables. The regions of allowed parameterization differ greatly, especially in the power law case, between the two models, and predictions for $N_\text{r}$ can differ by as much as a factor of ten for specific parameterizations. Predictions by $R_\text{r}$ differ by as much as a factor of three. This is in part because bright pulsars distant from Earth have lower flux, and therefore can appear unresolved in the position-dependent sensitivity model, but the step function sensitivity model always marks these pulsars as unresolved. The difference is also caused by the fact that lower sensitivity is correlated with MSP population density, a fact not appreciated by the step function model. The GCE log normal luminosity function differs most between sensitivity models, most likely due to \comment{its thinness and low mean, but I need to think more about exactly why this is.}

@@

In contrast, the smoothed sensitivity model does not appear to differ from the position-dependent sensitivity model by nearly as much. \comment{Except the power law, which may be a bug? I just checked; I don't think it's a bug.} This is likely because the smoothed sensitivity model differs from the position dependent model only for MSPs near $F_\text{th}(\ell, b)$, which is a relatively small number of MSPs for most luminosity functions. Motivated by this similarity and the greater computational complexity of the smoothed sensitivity model, we will mostly use the position-dependent sensitivity model throughout the rest of this study.

@@

Plots of $N_\text{r}$, $R_\text{r}$, and $N_\text{GCE}$ for different parameterizations of the power law and log normal luminosity functions are shown in figure \ref{fig:sensitivity-results}, and values for $N_\text{r}$ and $R_\text{r}$ for specific parameterizations are given in table \ref{tab:sensitivity-values}. The number of sources in the GCE does not depend on the telescope's sensitivity, so $N_\text{GCE}$ is not included in table \ref{tab:sensitivity-values} and is only included in fig. \ref{fig:sensitivity-results} for reference. \comment{That means that the backgrounds of the column plots do not change from plot to plot. I could put them all on the same axes.}

@@

The flux ratio as computed by equation \ref{eqn:roi-conversion} between our region and the same $40^\circ \times 40^\circ$ without the Galactic disk cutout is 1.90. Similarly, the ratio is 1.70, 1.44,1.26, 1.04, and 0.869 for a $30^\circ \times 30^\circ $, $20^\circ \times 20^\circ$, $15^\circ \times 15^\circ$, $10^\circ \times 10^\circ$, and $7^\circ \times 7^\circ$ respectively. We mention $15^\circ \times 15^\circ$ because it is the ROI used by ref. \cite{Ajello:2015kwa}, and $7^\circ \times 7^\circ$ because it is used by refs. \cite{Abazajian:2014fta} and \cite{Gordon13}.

@@

\section{Calculation of photon energy}
\label{app:photon-energy}
The parameterization of the NPTF luminosity function of ref. \cite{Lee:2015fea} is given with flux units of photons per second. To convert this to luminosity via appendix \ref{app:lum-to-flux}, we need to find the energy of a single GCE photon. To do this, we fit a broken power law to the GCE spectrum found by di Mauro and described in section \ref{sec:total-lum}, defining the flux observed from photons in an energy bin of energy $E_\gamma$ and width $dE_\gamma$ as $dF = E_\gamma N(E_\gamma)dE_\gamma$. The function $E_\gamma^2 N(E_\gamma)$ is plotted in figure \ref{fig:di-mauro-example}. The average photon energy is then calculated by
\begin{equation}
    \langle E_\gamma \rangle =  \brackets{\int_{\SI{0.1}{\giga\electronvolt}}^{\SI{100}{\giga\electronvolt}} E_\gamma N(E_\gamma) dE_\gamma} \brackets{\int_{\SI{0.1}{\giga\electronvolt}}^{\SI{100}{\giga\electronvolt}} N(E_\gamma) dE_\gamma}^{-1} = \SI{1.58e-3}{\erg}.
    \label{eqn:photon-energy}
\end{equation}
However, for the conversion of the photon flux to energy flux for the NPTF luminosity function specifically, we use a spectrum extending from $\SI{1.893}{\giga\electronvolt}$ to $\SI{11.943}{\giga\electronvolt}$, which was used in the reference that derived the flux \cite{Lee:2015fea}. This yielded an energy of $\SI{5.76e-3}{\erg}$.

If the broken power law fit to the GCE spectrum proposed by Calore et al. is used, then the energy per photon over the $\SI{0.1}{\giga\electronvolt}$ to $\SI{100}{\giga\electronvolt}$ spectrum is $\SI{1.41e-3}{\erg}$. If the fit to the Zhong et al. 2020 spectrum with $\gamma=1.2$ is used, then the photon energy is $\SI{1.35e-3}{\erg}$. We see then that the photon energy, while highly sensitive to the range of spectrum used, is not very sensitive to the GCE spectrum used.

@@

\bibliographystyle{unsrt}
\bibliography{gce.bib}
